---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# parkhoppr

[![Travis-CI Build Status](https://travis-ci.org/LucyMcGowan/parkhoppr.svg?branch=master)](https://travis-ci.org/LucyMcGowan/parkhoppr)

The goal of parkhoppr is to allow access to Disney World wait times.

## Installation

You can install parkhoppr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LucyMcGowan/parkhoppr")
```

## Example

There is currently just one function - you can get wait times for rides at Disney World✨. 

```{r example}
## load the library
library("parkhoppr")
## by default, get_wait_times() outputs Magic Kingdom wait times
get_wait_times()
```

You can specify the Disney World park you would like to retrieve wait times for using the `park` parameter.

```{r}
get_wait_times(park = "hollywood_studios")
```


## have some fun!
```{r, message = FALSE, warning = FALSE}
library("dplyr")
library("ggplot2")
get_wait_times() %>%
  filter(fast_pass == TRUE) %>%
  mutate(wait_cat = case_when(
    wait_time >= 45 ~ "bad",
    wait_time >= 25 & wait_time < 45 ~ "ok",
    wait_time < 25 ~ "good"
  )) %>%
  arrange(wait_time) %>%
  mutate(name = forcats::fct_reorder(name, wait_time)) %>%
  ggplot(aes(name, wait_time, fill = wait_cat)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        plot.margin = unit(c(0.1, 0.1, 0.1, 2), "cm")) +
  xlab("") +
  ylab("wait time")
```



*Shout out to the [themeparks](https://github.com/cubehouse/themeparks) library that inspired this little jaunt!*
